---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MMLCA

<!-- badges: start -->

<!-- badges: end -->

**MMLCA** aims to simplify the identification of multimorbidity patterns through user-friendly functions. Leveraging the power of Latent Class Analysis (LCA) as implemented in the `poLCA` package, **MMLCA** provides an accessible and efficient tool for researchers.

## Installation

You can install the development version of MMLCA from [GitHub](https://github.com/) with:

```{r,eval=FALSE}
# install.packages("devtools")
devtools::install_github("ARCbiostat/MMLCA")
```

## Overview of the package

For the index of all functions, please visit the [Reference Documentation](docs/reference/index.html).

## Example

This is an example with all the steps to identify MM patterns using LCA.

### Preparation

Load the package and the data:

```{r example}
library(MMLCA)
data(mmdata)
```

Prepare the dataset:

```{r}
X <- prepare_data(mmdata, dis_string = "dis", keepmm = T)
```

The chronic diseases data has 2761 subjects since we removed individuals with only one chronic condition.

Select the conditions to include in the LCA based on the prevalence:

```{r}
threshold <- 0.02 # 2% prevalence
disease_names <- select_conditions(X,
  threshold = threshold
)

disease_names
```

Divide the data in train/test

```{r}
set.seed(202112)
train <- sample(1:nrow(X), round(nrow(X) * 0.7))
test <- setdiff(1:nrow(X), train)
```

### Run the LCA

Run the LCA with different number of classes and compare the metrics:

```{r,results='hide'}
res <- select_number_LCA(
  nclasses = 2:7,
  X = X[train, ],
  conditions = disease_names,
  nrep = 5
)
```

**Note**: a higher number of repetitions may be needed. Default is 50. See the documentation for further details.

Compare the classification accuracy on the train vs. test data:

```{r}
ggacc <- ggaccuracy_LCA(res, test = X[test, ])
```

### Interpretation of the MM patterns

We now consider the result with 5 classes and try different method to characterize the patterns in terms of over expressed diseases.

**Method 1:** O/E and Exclusivity:

```{r,fig.height=50,fig.width=20}

OEx_sol5 <- ggOEx(res$obj[[4]], table = F)

```

**Method 2:** O/E and overall prevalence:

```{r,fig.height=20}

OE_sol5 <- ggOE(res$obj[[4]], table = F)

```

Same method but with 95% CI:

```{r,fig.height=20}
OEx_sol5 <- ggOE(res$obj[[4]], table = F,boot = T)
```



**Method 3:**

```{r,fig.height=20}

prev_sol5 <- ggprev(res$obj[[4]])

```

**Method 4:**

```{r,fig.height=10,fig.width=50}

prev_sol5 <- ggprev_spaghetti(res$obj[[4]])

```

### Assignment of subjects into the latent classes

**Warning**: If additional analyses are performed, it is recommended to take into account for the uncertainty in the classification.

```{r}
mm_pattern <- assign_LCA(res$obj[[4]],X)
table(mm_pattern)
```
