---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MMLCA

<!-- badges: start -->

<!-- badges: end -->

**MMLCA** aims to simplify the identification of multimorbidity patterns through user-friendly functions. Leveraging the power of Latent Class Analysis (LCA) as implemented in the `poLCA` package, **MMLCA** provides an accessible and efficient tool for researchers.

## Installation

You can install the development version of MMLCA from [GitHub](https://github.com/) with:

```{r,eval=FALSE}
# install.packages("devtools")
devtools::install_github("ARCbiostat/MMLCA")
```

## Overview of the package

```{r,echo=FALSE}

# Get the namespace of the package
ns <- asNamespace("MMLCA")

# List all exported functions
exported_functions <- ls(ns, all.names = TRUE)

# Filter to include only functions
exported_functions <- Filter(function(x) is.function(get(x, envir = ns)), exported_functions)

exported_functions <- exported_functions[-c(1:4)]

# Get descriptions for each exported function
get_description <- function(func_name) {
help_content <- capture.output(help(func_name, package = "MMLCA"))
description <- help_content[grep("Description", help_content, ignore.case = TRUE)]
paste(description, collapse = " ")
}


# Print the exported functions and descriptions in Markdown format
cat(paste0("* **", exported_functions, "**: ", sapply(exported_functions, get_description), collapse = "\n"))


```

## Example

This is a basic example:

```{r example}
library(MMLCA)
```
